

\setstretch{1}
\pdfbookmark[1]{Acknowledgments}{acknowledgments}



\begingroup
\let\clearpage\relax
\let\cleardoublepage\relax





I take the honour and privilege to express my deep sense of gratitude to my esteemed guide 
\textbf{Dr Debadatta Pati}, Assistant Professor of ECE Department, National institute of technology Nagaland
for his scholarly instructive guidance, support and continued
encouragement throughout my work.
Without our inspiring discussions on certain issues
at times, I would have never been able to complete this work.
I greatly admire his attitude
towards research, creative thinking, hard work and dedication.

I thank the Head of the Department, \textbf{Dr P. Chinnamuthu} and other faculty members for their
help and support in carrying out my work. My thanks go to \textbf{Mr. Madhusudan Singh} sir and \textbf{Krishna Dutta} sir for 
providing an excellent facility and maintaining a good ambience in the Speech processing and pattern recognition (SPPRC) lab to carry out my work.
Their friendly and helpful nature has made my work easy.

I also like to thank Department of Electronics and Information Technology (DeitY), Govt. of India for providing financial support, as my work is the part of ongoing DeitY sponsered project title "Development of Excitation Source Features Based Spoof Resistant and Robust Audio-Visual Person Identification System".

 Finally, I must express my very profound gratitude to my parents for providing me with unfailing support and continuous encouragement
 throughout my years of study and through the process of researching. This accomplishment would not have been possible without them.

\vspace{1.5cm}
\begin{center}
\noindent \begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}} \textbf{}  & \textbf{Sincerely} \\ & \textbf{\authorName}  \end{tabular*}
\end{center}

\endgroup

